Communication-efficient Learning from Multiple Experts

### 2017-05-10 draft/draft.tex
paper update

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2012} with
% \usepackage[nohyperref]{icml2012} above.
\usepackage{hyperref}

@@

$$ L(w,v)= -\frac{1}{N} \sum_{n=1}^N (y_n \log \sum_{i=1}^M v_i\hat{y}_{ni} + (1-y_n) \log(1-\sum_{i=1}^M v_i \hat{y}_{ni})) + \psi \sum_{i=1}^{M} (y_{ni} - z_{ni})^2+\lambda \mid v \mid$$

$$ \sum_{i=1}^{M} v_i = 1 $$

where $y_n$ are ground truth labels for all training samples, $\hat{y}_{ni}$ are labels retrieved by querying  current client models, $z_{ni}$ are training labels from annotator clients, $v_i$ is a normalized vector of weights for all the clients.

@@

The gradient is defined with the following equations:

$$ \frac{\partial L}{\partial w_j} = -\frac{1}{N} \sum_{n=1}^N (y_n \frac{1}{\sum_{i=1}^M v_i \hat{y}_{ni}} v_j \frac{\partial y_n}{\partial w_j} + (1-y_n) \frac{1}{1-\sum_{i=1}^M } v_j \frac{\partial y_n}{\partial w_j} + \psi \sum_{i=1}^M 2 (y_{ni} - z_{ni} \frac{\partial y_n}{\partial w_j}  ))$$

$$ \frac{\partial L}{\partial v_i} =  -\frac{1}{N} \sum_{n=1}^N (y_n \frac{1}{\sum_{i=1}^M v_i y_{ni}} + (1-\hat{y_n}) \frac{1} {1-\sum_{i=1}^M v_i y_{ni}} (-y_n) $$

The expression for the gradient $ \frac{y_n}{w_j}$ depends on the concrete method used to model the annotators.

@@

In order to still use gradient descent as a convex optimization method with the $L_1$ norm, we use the method of subgradient when updating the value of $v$. The update that we derived is the following:

$$ v= v + S_{\lambda} (x-t_s \frac{y_n}{v}, \lambda)$$

where
$$ S_{\lambda} = 
\left\{
	\begin{array}{ll}
		x-\lambda  & \mbox{if } x > \lambda  \\
		x+\lambda & \mbox{if } x < -\lambda \\
		0 & \mbox{otherwise}
	\end{array}
\right.
$$

@@

$$ v = \frac{v}{\sum_{i=1}^M v_i} $$

@@

>>>>

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2012} with
% \usepackage[nohyperref]{icml2012} above.
\usepackage{hyperref}

@@

\begin{equation}
\begin{split}
 L(w,v)= -\frac{1}{N} \sum_{n=1}^N (\hat{y}_n \log \sum_{i=1}^M v_i y_{ni} + (1-\hat{y}_n) \log(1-\sum_{i=1}^M v_i y_{ni})) + \\ \psi \sum_{i=1}^{M} (y_{ni} - z_{ni})^2+\lambda \mid v \mid
\end{split} 
\end{equation}

\begin{equation}
\sum_{i=1}^{M} v_i = 1 
\end{equation}

where $ \hat{y}_n $ are ground truth labels for all training samples, $ y_{ni} $ are labels retrieved by querying  current client models, $z_{ni}$ are training labels from annotator clients, $v_i$ is a normalized vector of weights for all the clients. The final loss function consists of a crossentropy calculation for the empirical loss with respect to the ground truth, the quadratic loss with respect to the client annotations weighted by a parameter $\phi$ and the 1-norm of the parameter vector $v$ weighted by another parameter $\lambda$.

@@

The gradient is defined with the following equations:
\begin{equation}
\begin{split}
 \frac{\partial L}{\partial w_j} = -\frac{1}{N} \sum_{n=1}^N (y_n \frac{1}{\sum_{i=1}^M v_i \hat{y}_{ni}} v_j \frac{\partial y_n}{\partial w_j} + (1-y_n) \frac{1}{1-\sum_{i=1}^M } v_j \frac{\partial y_n}{\partial w_j} + \\  \psi \sum_{i=1}^M 2 (y_{ni} - z_{ni} \frac{\partial y_n}{\partial w_j}  ))
\end{split}
\end{equation}

\begin{equation} \frac{\partial L}{\partial v_i} =  -\frac{1}{N} \sum_{n=1}^N (y_n \frac{1}{\sum_{i=1}^M v_i y_{ni}} + (1-\hat{y_n}) \frac{1} {1-\sum_{i=1}^M v_i y_{ni}} (-y_n) 
\end{equation}
The expression for the gradient $ \frac{y_n}{w_j}$ depends on the concrete method used to model the annotators.

@@

In order to still use gradient descent as a convex optimization method with the $L_1$ norm, we use the method of subgradient when updating the value of $v$. The update that we derived is the following:
\begin{equation}
 v= v + S_{\lambda} (x-t_s \frac{y_n}{v}, \lambda)
\end{equation}
where
\begin{equation}
S_{\lambda} = 
\left\{
	\begin{array}{ll}
		x-\lambda  & \mbox{if } x > \lambda  \\
		x+\lambda & \mbox{if } x < -\lambda \\
		0 & \mbox{otherwise}
	\end{array}
\right.
\end{equation}

@@

\begin{equation}
v = \frac{v}{\sum_{i=1}^M v_i}
\end{equation}

@@

We use two datasets to evaluate our methodology of combining the expertise of different annotators. Furthermore, we test our approach using two different models of annotators: logistic regression model and a neural network model (perceptron with one hidden layer).

\subsection{Datasets}
In order to evaluate our approach, we used one dataset with real-life data and one synthetic dataset. We obtained a real-life dataset from the authors of a related paper about learning to predict from crowdsourced data by Bi et al.~\cite{bi2014learning}. This dataset consists of results from an experiment with 21 workers at the \textit{Amazon Mechanical Turk}. These workers executed 10 tasks, all of the tasks being binary classification of images between two types of dogs. Since each worker has different expertise, the challenge is to determine the subset of highly competent workers and combine their abilities for a superior classification system.

Synthetic dataset was created using a method similar to the one used by Huang et al.~\cite{xiao2013learning}. The dataset consists of 1-dimensional data, random points between $0$ and $2\pi$, also labeled using randomization. We generate a ground truth based on random noise superpositioned over a nonlinear function:

\begin{equation}
f_n = 10\sin(6x)\sin(x/2)
\end{equation}

In order to get proper labels for our data instead of this nonlinear function, we need to additionaly put the values of the function $f_n$ through a sigmoid function:

\begin{equation}
\sigma(x) = \frac{1}{1+e^t}
\end{equation}

Finally, we take the values higher than $0.5$ as $1$, while the other values correspond to label $0$.

\subsection{Sensitivity to the weight of the regularization}

In the beginning, we examine the changes of the loss function when increasing the parameter $\lambda$ from 0 to 1, thereby adding the weight to the sparsity part of the loss function. The results of this test are displayed on Figure~\ref{}.

\subsection{Optimization process}

Furthermore, we look at how the value of the loss function changes while the optimization is running. We plot the loss against the number of iteration, which shows the steep decline of the loss value. This shows that using our gradient-based procedure we can get fast to a very accurate classification system. The graph is shown on Figure~\ref{}.

Next, we execute a similar test with the parameter $v$. We look at how the number of nonzero elements of $v$ changes while optimization is running. In other words, we examine how the optimizer selects the competent annotators.

\subsection{Synthetic data}

In this subsection we show the classification performance on our synthetically generated data.
